---
title: "API"
output:
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, message = F, warning = F)
library(knitr)
library(reticulate)
```

We're using [plumber](https://www.rplumber.io/) to build the application programming interface to the database here:

https://api.calstartdata.org

## Browser

To try it yourself, please visit the [API](https://api.calstartdata.org), expand any of the interfaces and click on "Try it out". 

## Command line

This will show the command using [curl](https://curl.haxx.se) to fetch the data:

```{bash}
curl -s "https://api.calstartdata.org/projects"
```

```{bash}
curl -s "https://api.calstartdata.org/project/1"
```

The data is formatted as [JSON](https://www.w3schools.com/whatis/whatis_json.asp), which allows for flexible hierarchical data structures that are both human and machine readable. These JSON structures can be rendered into native programming language data structures, such as data frames, that can be further manipulated.

## R

Here's an example of how you might programmatically access the data in R using the [jsonlite](https://cran.r-project.org/web/packages/jsonlite/vignettes/json-apis.html) library:

```{r}
projects <- jsonlite::fromJSON("https://api.calstartdata.org/projects")
knitr::kable(projects)

knitr::kable(jsonlite::fromJSON("https://api.calstartdata.org/project/1"))
```

## Python

And from Python:

```{r python install, eval=F, echo = F}
# one time install
install.packages("reticulate")
# yes, install Miniconda
library(reticulate)
py_install("pandas")
```

```{python}
import pandas

projects = pandas.read_json("https://api.calstartdata.org/projects")

project_1 = pandas.read_json("https://api.calstartdata.org/project/1")
```

Since this web page is rendered in Rmarkdown, we'll show the contents of the Python data frames using the same R function as for the R example above, getting the Python objects using the R library [reticulate](https://rstudio.github.io/reticulate/articles/r_markdown.html#calling-python-from-r-1):

```{r}
library(reticulate)

knitr::kable(py$projects)
knitr::kable(py$project_1)
```




