---
title: "Reports"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
fmt <- knitr::opts_knit$get("rmarkdown.pandoc.to") # html latex docx
if (fmt != "html"){
  knitr::opts_chunk$set(echo = F, warning = F, message = F)
} else {
  knitr::opts_chunk$set(echo = T, warning = F, message = F)
}
```

Reports can extract data from the API for automated generation of text, figures (maps, time series, etc) and tables in a variety of formats (html, pdf, docx). This is especially made possible with Rmarkdown (see 1 min video: [What is R Markdown? on Vimeo](https://vimeo.com/178485416)).

This web page reports.**html** was rendered from [reports.**Rmd**]( https://github.com/CALSTART/calstartdata.org/blob/master/reports.Rmd) which can also be rendered in these other formats:

- Adobe: [reports.**pdf**](./reports.pdf)
- Word: [reports.**docx**](./reports.docx)

## Projects

```{r}
library(jsonlite)
library(knitr)
library(kableExtra)
library(glue)
library(stringr)

# helper functions ----
str_trunc <- function(s, nchar_max = 20){
  if (nchar(s) > nchar_max){
    s <- str_sub(projects$name[1], end=nchar_max) %>% 
      paste0("...")
  }
  return(s)
}

kbl <- function(tbl){
  if (fmt != "html"){
    out <- kable(tbl) 
  } else {
    out <- kable(tbl) %>%
      kable_styling(bootstrap_options = c("striped", "hover"))
  }
  out
}

# projects ----
projects <- fromJSON("https://api.calstartdata.org/projects")
kbl(projects)
```

### 1. `r str_trunc(projects$name[1])`

Full Project Name: `r projects$name[1]`

#### Vehicles

```{r}
fromJSON("https://api.calstartdata.org/project/1/vehicles") %>% 
  kbl()
```


### 2. `r str_trunc(projects$name[2])`

#### Vehicles

```{r}
fromJSON("https://api.calstartdata.org/project/2/vehicles") %>% 
  kbl()
```

